# Code-a-thon Project Template

This project is intended to help you apply your skills in R in a way that would be conducive for collaborating or creating reproducible analyses.


## Data Used

Identify a dataset to analyze. Remember that if you share the data you must **not violate any privacy restrictions**

If you don't have your own data, options for places to find data are listed on https://daseh.org.

You might start by setting up an R Project, importing your data, previewing the data, etc. 

```{r}
library(tidyverse)
who<-read_csv(file="2322814_ALL_LATEST.csv")
who
colnames(who)
who1<- who %>% rename(year = DIM_TIME)
who1
who2<- who1 %>% rename(country = DIM_GEO_CODE_TYPE)
who2
```

**describe** what your data looks like and **where** you got it. Identify what the variables and samples are, or point to a data dictionary. Describe how the data was originally created. 
#38,424 rows and 16 columns of data
# data from WHO database
# World Health Organizatin TB data

# Data Cleaning/Wrangling

Perform any data subsetting, cleaning, or manipulation methods that were described in this course on your data. Examples are: renaming the columns, recoding values, reshaping the data, filtering the data etc. 

You might also research other methods to include here, especially if your data is very unique.

```{r}
filter(who2)
```


# Data Visualization

Create some visualizations of your data using the esquisse app or the ggplot2 package.

```{r}
library (tidyverse)
who2 %>% filter(GEO_NAME_SHORT == "Egypt" |GEO_NAME_SHORT== "Tunisia") %>%
ggplot( aes(x = year, y = RATE_PER_1000_N, color=GEO_NAME_SHORT))+
  geom_point()+
  geom_line() +
  facet_grid(~DIM_SEX)


library(esquisse)

```


```{r}
count (who2, IND_NAME)
count (who2, GEO_NAME_SHORT)
```


# Data Analysis

Perform a **simple analysis** of your data. This can involve summarizing the data to describe aspects about it (quartiles, means, range etc.) or a simple statistical test. 

Don't forget to describe what analysis you performed and why. Provide some simple **interpretation** about what your analysis might indicate about your data.

```{r}

```


# Please include additional sections as desired.

```{r}

```


# Versions

Include some information about the version of R and the packages you are using by running sessionInfo().

```{r}
sessionInfo()
```

Render your document to an html or pdf using the "Knit" button.
